FTLR proof cases

### 2018-06-27 fully-abstract-comp/ftlr-proof-cases.tex
Initial work on the FTLR xjmp case.

@@

@@

  We have that
  \begin{itemize}
  \item $\Phi_S \step[\gc] \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
  \item One of the following holds
    \begin{enumproof}
    \item(jmp,jnz) $\Phi_S' = \Phi_S\updReg{\pcreg,r_1}{\Phi_S(r_1),w_1}$ and
      $\Phi_T' = \Phi_T\updReg{\pcreg,r_1'}{\Phi_T(r_1),w_1'}$ and
      $\Phi_S(r_1) = \Phi_T(r_1) = ((\perm_1,\lin_1),\baddr_1,\eaddr_1,\aaddr_1)$,
      $\exec{\Phi_S(r_1)}$, $\withinBounds{\Phi_S(r_1)}$,
      $w_1 = \linCons{\Phi_S(r_1)}$ and $w_1' = \linCons{\Phi_T(r_1)}$
    \item(xjmp) $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) =
      \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and
      $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and
      $c_1' \neq \retptrc(\_)$ and $c_2' \neq \retptrd(\_)$ and
      $\Phi_S'' = \Phi_S\updReg{r_1,r_2}{\linCons{c_1},\linCons{c_2}}$ and $\Phi_S' = \xjumpResult{c_1}{c_2}{\Phi_S''}$ and
      $\Phi_T'' = \Phi_T\updReg{r_1,r_2}{\linCons{c_1'},\linCons{c_2'}}$ and
      $\Phi_T' = \xjumpResult{c_1'}{c_2'}{\Phi_T''}$
    \end{enumproof}
  \end{itemize}

@@

  In the second case (xjmp), blabla
  TODO
\end{proof}

>>>>

\begin{lemma}
  \label{lem:sealed-lrv-lrexj}
  If
  \begin{itemize}
  \item $\npair{(\sealed{\sigma,\vsc_1},\sealed{\sigma,\vsc_1'})} \in \lrvg{\trust}(W_{R,1})$
  \item $\npair{(\sealed{\sigma,\vsc_2},\sealed{\sigma,\vsc_2'})} \in \lrvg{\trust}(W_{R,2})$ 
  \item $\nonExec{\vsc_1'}$ and $\nonExec{\vsc_2'}$
  \item $W_{R,1} \oplus W_{R,2}$ is defined
  \end{itemize}
  Then
  \begin{itemize}
  \item $\npair{(\vsc_1,\vsc_2,\vsc_1',\vsc_2')} \in \lrexj(W_{R,1}\oplus W_{R,2})$
  \end{itemize}
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

        $\nonExec{\Phi_S(r_2)}$ and $\nonExec{\Phi_T(r_2)}$ and

@@

  We have that
  \begin{itemize}
  \item $\Phi_S \step[\gc] \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S$ does not point to $\scall{\offpc,\offsigma}{r_1}{r_2}$ or $\txjmp{r_1}{r_2}$
  \item One of the following holds
    \begin{enumproof}
    \item(jmp,jnz) $\Phi_S' = \Phi_S\updReg{\pcreg,r_1}{\Phi_S(r_1),w_1}$ and
      $\Phi_T' = \Phi_T\updReg{\pcreg,r_1'}{\Phi_T(r_1),w_1'}$ and
      $\Phi_S(r_1) = \Phi_T(r_1) = ((\perm_1,\lin_1),\baddr_1,\eaddr_1,\aaddr_1)$,
      $\exec{\Phi_S(r_1)}$, $\withinBounds{\Phi_S(r_1)}$,
      $w_1 = \linCons{\Phi_S(r_1)}$ and $w_1' = \linCons{\Phi_T(r_1)}$
    \item(xjmp) $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) =
      \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and
      $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and
      $c_1' \neq \retptrc(\_)$ and $c_2' \neq \retptrd(\_)$ and
      $\nonExec{\Phi_S(r_2)}$ and $\nonExec{\Phi_T(r_2)}$ and
      $\Phi_S'' = \Phi_S\updReg{r_1,r_2}{\linCons{c_1},\linCons{c_2}}$ and $\Phi_S' = \xjumpResult{c_1}{c_2}{\Phi_S''}$ and
      $\Phi_T'' = \Phi_T\updReg{r_1,r_2}{\linCons{c_1'},\linCons{c_2'}}$ and
      $\Phi_T' = \xjumpResult{c_1'}{c_2'}{\Phi_T''}$
    \end{enumproof}
  \end{itemize}

@@

  In the second case (xjmp), we have that $\npair{(\Phi_S(r_1),\Phi_T(r_1))} \in \lrvg{\trust}(W_{R,1})$, $\npair{(\Phi_S(r_2),\Phi_T(r_2))} \in \lrvg{\trust}(W_{R,2})$ and $\npair{(\Phi_S'',\Phi_T'')} \in \lrrg{\trust}(W_R')$ for some $W_{R,1}, W_{R,2}, W_R'$ with $W_R = W_{R,1} \oplus W_{R,2} \oplus W_R'$.

  Using the facts that $\Phi_S(r_1) = \sealed{\sigma,c_1}$ and $\Phi_S(r_2) = \sealed{\sigma,c_2}$ and $\Phi_T(r_1) = \sealed{\sigma,c_1'}$ and $\Phi_T(r_2) = \sealed{\sigma,c_2'}$ and $\nonExec{\Phi_S(r_2)}$ and $\nonExec{\Phi_T(r_2)}$, and the above points, Lemma~\ref{lem:sealed-lrv-lrexj} tells us that $\npair{(c_1,c_2,c_1',c_2')} \in \lrexj(W_{R,1} \oplus W_{R,2})$.

  TODO
\end{proof}
